Fail Faster

### 2025-03-14 paper/paper.tex
some more work

\subsection{Property-Based Testing}
\jwc{Usual spiel about pbt and generators: here's the BQ generator library, it has return and bind, this is what they're for.}

@@

\jwc{Todo: Thia}

@@

\jwc{NOTE: we should test generator speed across both languages, but speed -> bugfinding ability in only OCaml.}
\jwc{
  Baseline generators to test speed in both languages:
  \begin{itemize}
    \item Single int
    \item Pair of ints, constrained
    \item List of ints
  \end{itemize}
}
\subsection{Impact on bug-finding ability}
\section{Conclusion \& Future Work}
\section{Related Work}
\jwc{A generator is a parser of randomness, and people have implemented lots of staged parser libraries!}
%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{bib}

>>>>

\subsection{Property-Based Testing}
\jwc{Usual spiel about pbt and generators: here's a monadic generic generator library (but we're using BQ to illustrage), it has return and bind, this is what they're for.}
\jwc{You often want generators to generate for sparse precoditions so you can exercise a property reasonably well}

@@

\jwc{
  \begin{itemize}
    \item In PBT in practice, we learned that in many cases, programmers don't
    even write custom generators, instead relying on type-derived generators.
    \item These generators just produce arbitrary values of a given type, not necessarily enforcing validity conditions.
    \item Many generator
  \end{itemize}
}
\jwc{Todo: Thia}

@@

\jwc{NOTE: we should test generator speed across both languages, but speed -> bugfinding ability in only OCaml.}
\jwc{
  Baseline generators to test speed in both languages:
  \begin{itemize}
    \item Single int
    \item Pair of ints, constrained
    \item List of ints
  \end{itemize}
}
\subsection{Impact on bug-finding ability}
\jwc{Staging type-derived generators (which are the most commonly used ones) can turn a timeout into a found bug!}
\section{Conclusion \& Future Work}
\section{Related Work}
\jwc{A generator is a parser of randomness, and people have implemented lots of staged parser libraries!}
%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{bib}
